\textls[-0]{\thetitle}

### 2023-03-17 metatheory-condensed.tex
Reply the comment.

W-types are eliminated with the form $\Wrec{\wsig}{\lkg}{t}$, where $t$ is of a
W-type $\El{\wcode{\wsig}}$, and $\lkg$ is essentially an $n$-tuple of
case handlers for the $n$ constructors in~$\wsig$ (\ruleref{tm/wrec}).
Each case handler has a type of form $\CaseSig{A}{B}{T}$, where
$T$ is the motive of the recursion (\ruleref{tyeq/casety});
for simplicity, we model non-dependent motives for recursion.\YZ{Does "for recursion" here convey relevant information?}\EDJreply{no. I actually wanted to say "non-dependent motives for non-dependent recursion". Maybe change to "only model non-dependent motives"?}
The collection of case handlers~$\lkg$ encodes those defined and inherited
by an \lsti{FRecursion} command in our plugin.
We choose to type it with a linkage type $\TyLkg{\RecSig{\wsig}{T}}$
to avoid introducing non-dependent $n$-tuples, which linkages generalize.

>>>>

W-types are eliminated with the form $\Wrec{\wsig}{\lkg}{t}$, where $t$ is of a
W-type $\El{\wcode{\wsig}}$, and $\lkg$ is essentially an $n$-tuple of
case handlers for the $n$ constructors in~$\wsig$ (\ruleref{tm/wrec}).
Each case handler has a type of form $\CaseSig{A}{B}{T}$, where
$T$ is the motive of the recursion (\ruleref{tyeq/casety});
for simplicity, we model non-dependent motives for recursion.\YZ{Does "for recursion" here convey relevant information?}\EDJreply{no. I actually wanted to say "non-dependent motives for non-dependent recursion". Maybe change to "only model non-dependent motives"??}
The collection of case handlers~$\lkg$ encodes those defined and inherited
by an \lsti{FRecursion} command in our plugin.
We choose to type it with a linkage type $\TyLkg{\RecSig{\wsig}{T}}$
to avoid introducing non-dependent $n$-tuples, which linkages generalize.
